Constraints on tensor and scalar couplings from $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$

### 2015-07-08 tensor/draft/draft-tensor-op.tex
[draft-tensor-op.tex] changed section IV.E, some changes in conclusion

\begin{table*}
  \renewcommand{\arraystretch}{1.3}
  %\resizebox{\textwidth}{!}{
  \begin{tabular}{c|ccc}
  \hline
  data set
  & only $F_H^\mu$
  & $F_H^\mu$ + other
  & $F_H^\mu$ + other
  \\
  set of couplings
  & $\wilson{T,\,T5}$
  & $\wilson{T,\,T5}$
  & $\wilson{T,\,T5,\, 9,\,10}$
  \\
  \hline \hline
  $\mbox{Re}\,\wilson{T}$
  & $\quad$ $[-0.32,\, 0.16]$ ($[-0.52,\, 0.35]$) $\quad$
  & $\quad$ $[-0.29,\, 0.09]$ ($[-0.43,\, 0.27]$) $\quad$
  & $\quad$ $[-0.23,\, 0.14]$ ($[-0.39,\, 0.30]$) $\quad$
  \\
  $\mbox{Im}\,\wilson{T}$
  & $[-0.25,\, 0.24]$ ($[-0.44,\, 0.44]$)
  & $[-0.19,\, 0.21]$ ($[-0.37,\, 0.35]$)
  & $[-0.17,\, 0.22]$ ($[-0.33,\, 0.37]$)
  \\[0.1cm]
  $\mbox{Re}\,\wilson{T5}$
  & $[-0.25,\, 0.24]$ ($[-0.44,\, 0.44]$)
  & $[-0.19,\, 0.17]$ ($[-0.33,\, 0.33]$)
  & $[-0.18,\, 0.16]$ ($[-0.32,\, 0.32]$)
  \\
  $\mbox{Im}\,\wilson{T5}$
  & $[-0.24,\, 0.25]$ ($[-0.44,\, 0.45]$)
  & $[-0.21,\, 0.19]$ ($[-0.37,\, 0.35]$)
  & $[-0.20,\, 0.18]$ ($[-0.36,\, 0.35]$)
  \\
  \hline
  $|\wilson{T}|$, $|\wilson{T5}|$
  & $[0.13,\, 0.43]$ ($[0.03,\, 0.57]$)
  & $[0.09,\, 0.33]$ ($[0.02,\, 0.44]$)
  & $[0.10,\, 0.33]$ ($[0.02,\, 0.43]$)
  \\
  \hline
  \end{tabular}
%}
  \renewcommand{\arraystretch}{1.0}
  \caption{
     \label{tab:cTT5:1-dimCLs}
     The constraints on complex-valued $\wilson{T,\,T5}$ --- [upper] 1D-marginalized
     at 68\% (95\%) probability and [lower] 2D-marginalized --- when using
     measurements of $i)$ only $F_H^\mu$, $ii)$ $F_H^\mu$ and other data in
     \reftab{tab:observables} (except $\overline{\cal B}(B_s \to \bar\mu\mu)$), and $iii)$ allowing
     also complex-valud new physics contributions to $\wilson{9,\,10}$.
  }
\end{table*}

@@

In the following we consider a model-independent scenario as predicted by the SM
augmented by dimension six operators that respect the SM gauge group and are
composed out of SM fields. After the discovery of a scalar resonance at the LHC
that complies currently with all requirements of the Higgs particle in the SM
and the steadily rising lower bounds on new particle masses towards higher energies
from ATLAS and CMS such a scenario becomes more and more viable\footnote{\todo{
comment on Cata/Jung \cite{Cata:2015ltad}.}}.

A non-redundant set of dimension six operators of
this effective theory (SM-EFT) was given in \cite{Grzadkowski:2010es} and the
matching to the effective theory of $\Delta B = 1$ decays \refeq{eq:Heff} at the
scale $\mu \sim m_W$ of the order of the $W$-boson mass in \cite{D'Ambrosio:2002ex}
for vector couplings $\wilson{7,\,9,\,10}$. The matching for tensor
\refeq{eq:tensor:ops} and scalar \refeq{eq:scalar:ops} operators
\cite{Alonso:2014csa} shows that SM gauge groups impose the relations
\begin{align}
  \wilson{P}  & = -\wilson{S}\,, &
  \wilson{P'} & = \wilson{S'}\,, &
  \wilson{T}  & = \wilson{T5} = 0
\end{align}
on scalar and pseudo-scalar couplings and require tensor couplings to be
suppressed to the level of dimension eight operators. In consequence only two
scalar couplings $\wilson{S,\, S'}$ arise that scale as $\sim v^2/\Lambda_{\rm NP} \ll 1$
where $v^2$ denotes the scale of electroweak symmetry breaking and $\Lambda_{\rm NP}$
a high energy scale at which new physics generates these operators.

@@

@@

The most general fit of complex-valued tensorial and scalar couplings 
$\wilson{S,S',P,P',T,T5}$ in combination with complex-valued vectorial couplings
$\wilson{9,\,9',\,10,\, 10'}$ --- i.e. the combination of \refsec{sec:tensor}
and \refsec{sec:scalar} with same prior ranges --- does not yield very different
bounds. The changes are only small and in fact the bounds tend to be even more
stringent, because tensor and scalar couplings can contribute to $F_H^{\mu}$
only constructively --- see \refeq{eq:FH-dependence}.
As before ${\cal B}$'s of $B\to K^{(*)}\bar\mu\mu$ help to strengthen the
constraints on $\wilson{T,\, T5}$. This demonstrates that even in the case
of complex-valued couplings the data is able to constrain all real and imaginary
parts.

%
%
%--------+---------+---------+---------+---------+---------+---------+---------+
\subsection{ for $B\to K^* \bar\ell\ell$}

\begin{table*}
  \renewcommand{\arraystretch}{1.5}
  %\resizebox{\textwidth}{!}{
  \begin{tabular}{cc|c|ccc}
  \hline
    observable
  & $q^2$-bin [GeV$^2$]
  & SM
  & $T,\,T5,\,9,\,10,$
  & $S^{(')},\,P^{(')},\,9^{(')},\,10^{(')}$
  & $S^{(')},P^{(')},\,T,\,T5,\,9^{(')},10^{(')}$
  \\
  \hline \hline
  \multirow{2}{*}{$\tau_{B^0} \times J_{6c}$}
  & $[1.1,\, 6]$
  & $\simeq 0$
  & $(0.7_{-2.1}^{+1.7}) \cdot 10^{-9\;}$
  & $(0.0_{-2.1}^{+2.2}) \cdot 10^{-10}$
  & \eos{$( 0.71_{-1.98}^{+0.52}) \cdot 10^{-21}$}
  \\
  & $[15,\, 19]$
  & $\simeq 0$
  & $(2.1_{-6.2}^{+5.1}) \cdot 10^{-10}$
  & $(0.7_{-6.6}^{+5.4}) \cdot 10^{-11}$
  & \eos{$(-0.25_{-0.23}^{+0.72}) \cdot 10^{-21}$}
  \\
  \hline
  \multirow{2}{*}{$\tau_{B^0} \times (J_{1c} + J_{2c})$}
  & $[1.1,\, 6]$
  & $(3.54_{-0.66}^{+0.65}) \cdot 10^{-9\;}$
  & $(5.0_{-1.9}^{+1.7}) \cdot 10^{-9\;}$
  & $(2.9_{-0.5}^{+0.4}) \cdot 10^{-9\;}$
  & \eos{$(3.23_{-1.31}^{+2.36}) \cdot 10^{-21}$}
  \\
  & $[15,\, 19]$
  & $(1.72_{-0.16}^{+0.16}) \cdot 10^{-10}$
  & $(4.7_{-2.6}^{+3.3}) \cdot 10^{-9\;}$
  & $(1.9_{-0.7}^{+0.3}) \cdot 10^{-10}$
  & \eos{$(7.28_{-3.29}^{+5.17}) \cdot 10^{-21}$}
  \\
  \hline
  \multirow{2}{*}{$\tau_{B^0} \times (J_{1s} - 3 J_{2s})$}
  & $[1.1,\, 6]$
  & $(2.98_{-0.54}^{+0.63}) \cdot 10^{-10}$
  & $(1.9_{-1.1}^{+1.4}) \cdot 10^{-8\;}$
  & $(4.9_{-1.4}^{+1.6}) \cdot 10^{-10}$
  & \eos{$(2.00_{-0.97}^{+1.03}) \cdot 10^{-20}$}
  \\
  & $[15,\, 19]$
  & $(1.12_{-0.10}^{+0.10}) \cdot 10^{-10}$
  & $(7.1_{-3.8}^{+5.6}) \cdot 10^{-9\;}$
  & $(1.4_{-0.4}^{+0.3}) \cdot 10^{-10}$
  & \eos{$(9.29_{-4.54}^{+3.86}) \cdot 10^{-21}$}
  \\
  \hline \hline
  \multicolumn{2}{c|}{$A_{\Delta \Gamma}(B_s \to \bar\mu\mu)$}
  & 1
  & SM
  & $[-1,\, 1]$
  & $[-1,\, 1]$
  \\
  \hline
  \end{tabular}
%}
  \renewcommand{\arraystretch}{1.0}
  \caption{
     \label{tab:postdictions}
     The 68\% probability intervals of not yet measured angular observables in
     $B^0\to K^{*0}\bar\mu\mu$ integrated over $q^2$ bins at low- and high-$q^2$
     for several new physics scenarios respecting all the considered experimental
     constraints. The SM prior predictives are given too, where ``$\simeq 0$''
     indicates zero in the considered
     approximation, see text for more explanations.
  }
\end{table*}

Eventually, we present the yet allowed ranges due to non-standard tensor
and scalar couplings of the so far unmeasured angular observables $J_{6c}$,
$(J_{1s} - 3\, J_{2s})$ and $(J_{1c} + J_{2c})$ in $B\to K^*(\to K\pi)\bar\ell\ell$
in order to explore the potential of their future measurements in fits of the kind
pursued in this work. \todo{Find nice place to cite method of moments paper.}
The 68\% probability intervals are collected in \reftab{tab:postdictions}
for the various general scenarios, i.e. allowing for interference with non-zero
vector couplings, in \refsec{sec:tensor}, \refsec{sec:scalar}
and \refsec{sec:tensor:scalar} for $q^2$-integrated quantities
in the low- and high-$q^2$ bins $q^2\in [1.1,\, 6]$ GeV$^2$ and $q^2\in [15,\, 19]$
GeV$^2$, respectively. Their posterior distributions have been obtained from the
final posterior samples as explained in~\cite{Beaujean:2012uj}.

For comparison, the SM estimates are also given in \reftab{tab:postdictions}
multiplied by the $B^0$-meson life time $\tau_{B^0} = 1.519$~ps.
At low-$q^2$ they are of order ${\cal O}(10^{-9})$ for $(J_{1s} - 3\, J_{2s})$ and
$(J_{1c} + J_{2c})$, getting suppressed down to ${\cal O}(10^{-10})$ at high-$q^2$
due to the $m_\ell/\sqrt{q^2}$ dependence. In order to compare it to the typical
magnitude of vector couplings, note that for example the branching ratio of
$B\to K^*\bar\ell\ell$
\begin{align}
  \frac{1}{\tau_{B^0}} \frac{{\rm d}\BR}{{\rm d}q^2} & =
    \frac{2}{3} (3 J_{1s} - J_{2s}) + \frac{1}{3} (3 J_{1c} -  J_{2c})
\end{align}
is numerically of the order ${\cal O}(10^{-19})$ in the SM
\todo{check large SM uncertainty of 30\% at low-$q^2$}
\begin{equation}
\begin{aligned}
  \langle {\rm d}\BR/{\rm d}q^2 \rangle_{[1.1,\, 6]} & =
  \left(1.86_{-0.44}^{+0.53} \right) \cdot 10^{-7} \,,
\\
  \langle {\rm d}\BR/{\rm d}q^2 \rangle_{[15,\, 19]} & =
  \left(1.91_{-0.16}^{+0.16} \right) \cdot 10^{-7} \,,
\end{aligned}
\end{equation}
when integrated over low- and high-$q^2$ regions. On the other hand, $J_{6c}$
is strictly zero for the approximation adopted here. Non-zero contributions
can be generated by QED corrections or potentially from higher-dimensional
($d > 6$) $|\Delta B| = |\Delta S| = 1$ operators, leading to parametrical
suppression of $\alpha_e/(4 \pi)$ or $(m_b/m_W)^2$, respectively. Such a
suppression must be compared to potential suppression present for tensor
and scalar contributions in particular NP models in order to decide their
relevance. Our model-independent fits are still in a realm where such
considerations are insignificant since current experimental measurements, in
combination with theory uncertainties, do not impose yet too stringent
constraints on tensor and scalar couplings.

Beyond the SM, $J_{6c}$ can get of order ${\cal O}(10^{-21})$ in scenarios
involving tensor couplings and only ${\cal O}(10^{-23})$ in their absence.
Concerning $(J_{1c} + J_{2c})$ and $(J_{1s} - 3\, J_{2s})$, again substantial
deviations from the SM prediction are possible only in the presence of non-zero
tensor couplings. In this case enhancement by two orders of magnitude are
possible up to the ${\cal O}(10^{-20})$ at high-$q^2$ and also at low-$q^2$ in
the case of $(J_{1s} - 3\, J_{2s})$, always being consistent with all included
experimental constraints in \reftab{tab:observables}. In view of current
experimental precision of \eos{$20\%$} branching ratio measurements corresponding
to the \eos{${\cal O}(10^{-20})$} one can indeed hope for some sensitivity to
such large effects in $(J_{1c} + J_{2c})$ and $(J_{1s} - 3\, J_{2s})$ in future
measurements.

@@

We find that the experimental measurement of $F_H^\mu$
\begin{enumerate}
\item imposes by itself constraints on tensor couplings \eos{$|{\cal C}_{T,\,T5}|
  < 0.35\, (0.55)$} at 68\% (95\%) probability, superseding previous bounds.
  In combination with current data from $B\to K^* \bar\mu\mu$ and lattice
  $B\to K^*$ form factors they become tighter \eos{$|{\cal C}_{T,\,T5}^\mu| < 0.30\,
  (0.45)$}, even in the presence of non-standard contributions in vector
  couplings.
\item allows for the first time to bound all four scalar and pseudo-scalar
  couplings due to it's complementarity to $\overline{\cal B}(B_s \to \bar\mu\mu)$.
  Even when taking into account destructive interference with vector couplings
  \eos{$|\wilson{i} + \wilson{i'}| < 0.4\, (0.7)$ and $|\wilson{i} - \wilson{i'}| <
  0.1\, (0.2)$} for $i = S,P$ at 68\% (95\%) probability. Currently, the bounds
  from $F_H^\mu$ are not as strong as those from $\overline{\cal B}(B_s \to \bar\mu\mu)$
  by a factor four. In the future, measurements at LHCb and Belle II will
  further tighten the bounds. Moreover, measurements of $F_H^e$ ($\ell = e$)
  will provide constraints on scalar couplings in the electron channel in
  the lack of measurements of $B_s \to \bar{e}e$.
\item SM-EFT $\ldots$
\end{enumerate}

>>>>

\begin{table*}
  \renewcommand{\arraystretch}{1.3}
  %\resizebox{\textwidth}{!}{
  \begin{tabular}{c|ccc}
  \hline
  data set
  & only $F_H^\mu$
  & $F_H^\mu$ + other
  & $F_H^\mu$ + other
  \\
  set of couplings
  & $\wilson{T,\,T5}$
  & $\wilson{T,\,T5}$
  & $\wilson{T,\,T5,\, 9,\,10}$
  \\
  \hline \hline
  $\mbox{Re}\,\wilson{T}$
  & $\quad$ $[-0.32,\, 0.16]$ ($[-0.52,\, 0.35]$) $\quad$
  & $\quad$ $[-0.29,\, 0.09]$ ($[-0.43,\, 0.27]$) $\quad$
  & $\quad$ $[-0.23,\, 0.14]$ ($[-0.39,\, 0.30]$) $\quad$
  \\
  $\mbox{Im}\,\wilson{T}$
  & $[-0.25,\, 0.24]$ ($[-0.44,\, 0.44]$)
  & $[-0.19,\, 0.21]$ ($[-0.37,\, 0.35]$)
  & $[-0.17,\, 0.22]$ ($[-0.33,\, 0.37]$)
  \\[0.1cm]
  $\mbox{Re}\,\wilson{T5}$
  & $[-0.25,\, 0.24]$ ($[-0.44,\, 0.44]$)
  & $[-0.19,\, 0.17]$ ($[-0.33,\, 0.33]$)
  & $[-0.18,\, 0.16]$ ($[-0.32,\, 0.32]$)
  \\
  $\mbox{Im}\,\wilson{T5}$
  & $[-0.24,\, 0.25]$ ($[-0.44,\, 0.45]$)
  & $[-0.21,\, 0.19]$ ($[-0.37,\, 0.35]$)
  & $[-0.20,\, 0.18]$ ($[-0.36,\, 0.35]$)
  \\
  \hline
  $|\wilson{T}|$, $|\wilson{T5}|$
  & $[0.13,\, 0.43]$ ($[0.03,\, 0.57]$)
  & $[0.09,\, 0.33]$ ($[0.02,\, 0.44]$)
  & $[0.10,\, 0.33]$ ($[0.02,\, 0.43]$)
  \\
  \hline
  \end{tabular}
%}
  \renewcommand{\arraystretch}{1.0}
  \caption{
     \label{tab:cTT5:1-dimCLs}
     The constraints on complex-valued $\wilson{T,\,T5}$ --- [upper] 1D-marginalized
     at 68\% (95\%) probability and [lower] 2D-marginalized --- when using
     measurements of $i)$ only $F_H^\mu$, $ii)$ $F_H^\mu$ and other data in
     \reftab{tab:observables} (except $\overline{\cal B}(B_s \to \bar\mu\mu)$), and $iii)$ allowing
     also complex-valud new physics contributions to $\wilson{9,\,10}$. \fred{For 9,10,S,P,T,T5, the absolute value is in $[0.077,0.269] ([0.020, 0.379])$}
  }
\end{table*}

@@

In the following we consider a model-independent scenario as predicted by the SM
augmented by dimension six operators that respect the SM gauge group and are
composed out of SM fields only. After the discovery of a scalar resonance at the LHC
that complies currently with all requirements of the Higgs particle in the SM
and the steadily rising lower bounds on new particle masses towards higher energies
from ATLAS and CMS such a scenario becomes more and more viable.

A non-redundant set of dimension six operators of
this effective theory (SM-EFT) was given in \cite{Grzadkowski:2010es} and the
matching to the effective theory of $\Delta B = 1$ decays \refeq{eq:Heff} at the
scale $\mu \sim m_W$ of the order of the $W$-boson mass in~\cite{D'Ambrosio:2002ex}
for vector couplings $\wilson{7,\,9,\,10}$. The matching for tensor
\refeq{eq:tensor:ops} and scalar \refeq{eq:scalar:ops} operators
\cite{Alonso:2014csa} shows that SM gauge groups in conjunction with the linear
representation impose the relations
\begin{align}
  \label{eq:mEFT-constraints}
  \wilson{P}  & = -\wilson{S}\,, &
  \wilson{P'} & = \wilson{S'}\,, &
  \wilson{T}  & = \wilson{T5} = 0
\end{align}
on scalar and pseudo-scalar couplings and require tensor couplings to be
suppressed to the level of dimension eight operators. In consequence only two
scalar couplings $\wilson{S,\, S'}$ arise that scale as $\sim v^2/\Lambda_{\rm NP} \ll 1$
where $v^2$ denotes the scale of electroweak symmetry breaking and $\Lambda_{\rm NP}$
a high energy scale at which new physics generates these operators.

@@

It must be noted that relations \refeq{eq:mEFT-constraints} are a consequence
of embedding the Higgs in a weak doublet along with the Goldstone bosons.
For example choosing a non-linear representation of the scalar sector allows
for additional dimension six operators in the SM-EFT, such that $\wilson{S,S',P,P'}$
are all independent and tensor operators have non-vanishing couplings already
at dimension six \cite{Cata:2015lta}.

@@

The most general fit of complex-valued tensor and scalar couplings 
$\wilson{S,S',P,P',T,T5}$ in combination with complex-valued vector couplings
$\wilson{9,\,9',\,10,\, 10'}$ --- i.e. the combination of \refsec{sec:tensor}
and \refsec{sec:scalar} with same prior ranges --- does not yield very different
bounds. The changes are only small and in fact the bounds tend to be even more
stringent, because tensor and scalar couplings can contribute to $F_H^{\mu}$
only constructively --- see \refeq{eq:FH-dependence}.
As before branching-ratio measurements of $B\to K^{*}\bar\mu\mu$ help to strengthen
the constraints on $\wilson{T,\, T5}$. This demonstrates that even in the case
of complex-valued couplings the data is able to constrain all real and imaginary
parts.

%
%
%--------+---------+---------+---------+---------+---------+---------+---------+
\subsection{Angular observables in $B\to K^* \bar\ell\ell$}

\begin{table*}
  \renewcommand{\arraystretch}{1.5}
  %\resizebox{\textwidth}{!}{
  \begin{tabular}{cc|c|ccc}
  \hline
    observable
  & $q^2$-bin [GeV$^2$]
  & SM
  & $\quad T(5),\,9,\,10\quad$
  & $\quad S^{(')},\,P^{(')},\,9^{(')},\,10^{(')} \quad$
  & $\quad S^{(')},P^{(')},\,T(5),\,9^{(')},10^{(')}$
  \\
  \hline \hline
  \multirow{2}{*}{$\tau_{B^0} \times J_{6c}$}
  & $[1.1,\, 6]$
  & $\simeq 0$
  & $(0.7_{-2.1}^{+1.7}) \cdot 10^{-9\;}$
  & $(0.0_{-2.1}^{+2.2}) \cdot 10^{-\todo{10}}$
  & $(0.2_{-1.1}^{+1.2}) \cdot 10^{-9}$
  \\
  & $[15,\, 19]$
  & $\simeq 0$
  & $(2.1_{-6.2}^{+5.1}) \cdot 10^{-10}$
  & $(0.7_{-6.6}^{+5.4}) \cdot 10^{-11}$
  & $(-0.2_{-2.9}^{+3.5}) \cdot 10^{-11}$
  \\
  \hline
  \multirow{2}{*}{$\tau_{B^0} \times (J_{1c} + J_{2c})$}
  & $[1.1,\, 6]$
  & $(3.54_{-0.66}^{+0.65}) \cdot 10^{-9\;}$
  & $(5.0_{-1.9}^{+1.7}) \cdot 10^{-9\;}$
  & $(2.9_{-0.5}^{+0.4}) \cdot 10^{-9\;}$
  & $(2.8_{-1.0}^{+1.6}) \cdot 10^{-9}$
  \\
  & $[15,\, 19]$
  & $(1.72_{-0.16}^{+0.16}) \cdot 10^{-10}$
  & $(4.7_{-2.6}^{+3.3}) \cdot 10^{-9\;}$
  & $(1.9_{-0.7}^{+0.3}) \cdot 10^{-10}$
  & $(3.1_{-2.3}^{+2.5}) \cdot 10^{-9}$
  \\
  \hline
  \multirow{2}{*}{$\tau_{B^0} \times (J_{1s} - 3 J_{2s})$}
  & $[1.1,\, 6]$
  & $(2.98_{-0.54}^{+0.63}) \cdot 10^{-10}$
  & $(1.9_{-1.1}^{+1.4}) \cdot 10^{-8\;}$
  & $(4.9_{-1.4}^{+1.6}) \cdot 10^{-10}$
  & $(1.6_{-1.2}^{+0.9}) \cdot 10^{-8}$
  \\
  & $[15,\, 19]$
  & $(1.12_{-0.10}^{+0.10}) \cdot 10^{-10}$
  & $(7.1_{-3.8}^{+5.6}) \cdot 10^{-9\;}$
  & $(1.4_{-0.4}^{+0.3}) \cdot 10^{-10}$
  & $(5.3_{-3.8}^{+3.8}) \cdot 10^{-9}$
  \\
  \hline \hline
  \multicolumn{2}{c|}{$A_{\Delta \Gamma}(B_s \to \bar\mu\mu)$}
  & 1
  & SM
  & $[-1,\, 1]$
  & $[-1,\, 1]$
  \\
  \hline
  \end{tabular}
%}
  \renewcommand{\arraystretch}{1.0}
  \caption{
     \label{tab:postdictions}
     The 68\% probability intervals of not yet measured angular observables in
     $B^0\to K^{*0}\bar\mu\mu$ integrated over $q^2$ bins at low- and high-$q^2$
     for several new physics scenarios respecting all the considered experimental
     constraints. The SM prior predictives are given too, where ``$\simeq 0$''
     indicates zero in the considered
     approximation, see text for more explanations.
  }
\end{table*}

Eventually, we present the yet allowed ranges due to non-standard tensor
and scalar couplings of the so far unmeasured angular observables $J_{6c}$,
$(J_{1s} - 3\, J_{2s})$ and $(J_{1c} + J_{2c})$ in $B\to K^*(\to K\pi)\bar\ell\ell$
in order to explore the potential of their future measurements in fits of the kind
pursued in this work. 
The 68\% probability intervals are collected in \reftab{tab:postdictions}
for the various model-independent scenarios, allowing for interference with
non-zero vector couplings, in \refsec{sec:tensor}, \refsec{sec:scalar}
and \refsec{sec:tensor:scalar} for $q^2$-integrated quantities
in the low- and high-$q^2$ bins $q^2\in [1.1,\, 6]$ GeV$^2$ and $q^2\in [15,\, 19]$
GeV$^2$, respectively. Their posterior distributions have been obtained from the
final posterior samples as explained in~\cite{Beaujean:2012uj}.

For comparison, the SM estimates are also given in \reftab{tab:postdictions}
multiplied by the $B^0$-meson life time $\tau_{B^0} = 1.519$~ps.
At low-$q^2$ they are of order ${\cal O}(10^{-9})$ for $(J_{1s} - 3\, J_{2s})$ and
$(J_{1c} + J_{2c})$, getting suppressed down to ${\cal O}(10^{-10})$ at high-$q^2$
due to the $m_\ell/\sqrt{q^2}$ dependence. In order to compare it to the typical
magnitude of vector couplings, note that for example the branching ratio of
$B\to K^*\bar\ell\ell$
\begin{align}
  \frac{{\rm d}\BR}{{\rm d}q^2} & = \frac{\tau_{B^0}}{3} \left[
    2\, (3 J_{1s} - J_{2s}) + (3 J_{1c} -  J_{2c}) 
  \right]
\end{align}
is numerically of the order ${\cal O}(10^{-7})$ in the SM
\todo{check large SM uncertainty of 30\% at low-$q^2$}
\begin{equation}
\begin{aligned}
  \langle {\rm d}\BR/{\rm d}q^2 \rangle_{[1.1,\, 6]} & =
  \left(1.86_{-0.44}^{+0.53} \right) \cdot 10^{-7} \,,
\\
  \langle {\rm d}\BR/{\rm d}q^2 \rangle_{[15,\, 19]} & =
  \left(1.91_{-0.16}^{+0.16} \right) \cdot 10^{-7} \,,
\end{aligned}
\end{equation}
when integrated over low- and high-$q^2$ regions. On the other hand, $J_{6c}$
is strictly zero for the approximation adopted here. Non-zero contributions
can be generated by QED corrections or potentially from higher-dimensional
($d \geq 8$) $|\Delta B| = |\Delta S| = 1$ operators, leading to parametrical
suppression of $\alpha_e/(4 \pi)$ or $(m_b/m_W)^2$, respectively. Such a
suppression must be compared to potential suppression present for tensor
and scalar contributions in particular NP models in order to decide their
relevance. Our model-independent fits are still in a realm where such
considerations are insignificant since current experimental measurements, in
combination with theory uncertainties, do not impose yet too stringent
constraints on tensor and scalar couplings.

Beyond the SM, $J_{6c}$ can become of order ${\cal O}(10^{-9})$ in scenarios
involving tensor couplings and only ${\cal O}(10^{-10})$ in their absence.
Concerning $(J_{1c} + J_{2c})$ and $(J_{1s} - 3\, J_{2s})$, again substantial
deviations from the SM prediction are possible only in the presence of non-zero
tensor couplings. In this case enhancement by two orders of magnitude are
possible up to the ${\cal O}(10^{-8})$ at high-$q^2$ and also at low-$q^2$ in
the case of $(J_{1s} - 3\, J_{2s})$, always being consistent with all included
experimental constraints in \reftab{tab:observables}. In view of current
experimental precision of $20\%$ of the branching ratio measurements at LHCb
\cite{Aaij:2013iag} with only 1 fb$^{-1}$, corresponding to the ${\cal O}(10^{-8})$, one can
indeed hope for some sensitivity to such large effects in $(J_{1c} + J_{2c})$
and $(J_{1s} - 3\, J_{2s})$ for the not yet published 3 fb$^{-1}$ data set. 
\todo{Would be a nice place to cite method of moments paper?}

@@

We find that the experimental measurement of $F_H^\mu$
\begin{enumerate}
\item imposes by itself constraints on tensor couplings $|{\cal C}_{T,\,T5}|
  < 0.43\, (0.57)$ at 68\% (95\%) probability, superseding previous bounds.
  In combination with current data from $B\to K^* \bar\mu\mu$ and lattice
  $B\to K^*$ form factors they become tighter $|{\cal C}_{T,\,T5}| < 0.33\,
  (0.43)$, even in the presence of non-standard contributions in vector
  couplings.
\item allows for the first time to bound all four scalar and pseudo-scalar
  couplings due to it's complementarity to $\overline{\cal B}(B_s \to \bar\mu\mu)$.
  Even when taking into account destructive interference with vector couplings
  $|\wilson{i} + \wilson{i'}| < 0.3\, (0.6)$ and $|\wilson{i} - \wilson{i'}| <
  0.1\, (0.2)$ for $i = S,P$ at 68\% (95\%) probability. Currently, the bounds
  from $F_H^\mu$ are not as strong as those from $\overline{\cal B}(B_s \to \bar\mu\mu)$
  by about a factor four. In the future, measurements at LHCb and Belle II will
  further tighten the bounds.

  Moreover, measurements of $F_H^e$ ($\ell = e$)
  will provide constraints on scalar couplings in the electron channel in
  the lack of measurements of the branching ratio of $B_s \to \bar{e}e$.
\item SM-EFT $\ldots$
\end{enumerate}
